CS182: NBA Scheduler

### 2015-12-09 paper.tex
fix typo
fix formatting

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{courier}
\usepackage{multicol}
\usepackage{microtype} %required to fix courier linebreaking issues
\usepackage{hyperref} % make references into links
\usepackage{amsfonts}
\hypersetup{colorlinks=true, linkcolor=blue} %make them pretty links
\usepackage[all]{hypcap} %make them link to the right place
\usepackage{url}
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother
\usepackage{geometry}
\geometry{legalpaper, portrait, margin=1in}

@@

	The rationale here is the season is typically 160-170 days, meaning ideally each game is every other day. So, we specify the domain of possible dates for a game to be a window of dates centered at that ideal date. The heuristics used were as follows:
	\begin{enumerate}
		\item Forward checking was relatively straightforward in this CSP. We remove any True/False possibilities for any pair of teams if one team has reached the limit of home or away games for that matchup. For any date $d$ we assign for some game\_num, we remove the dates prior to $d$ for any game after game\_num, and any date after $d$ for any game before game\_num for any matchup involving one of these teams.
		\item Choosing what matchup to next assign was the most perplexing part of this problem. We initially chose the team with the most assignments up to that point - essentially trying to assign all home/away matchups for a specific team at a time. The difficulty in this CSP is finding the right assignments for matchups of teams that play 3 times. There's an added complexity of having the right combination of 1 home/2 away and 2 home/1 away matchups that keep each team's total home/away games even. What was originally happening was the DFS would assign every matchup for every team until the last few, but it was impossible to find a right assignment for them because too many teams had their 3-game matchups with a given 2-home or 2-aways. There wasn't a good backtracking method implemented once that happened, so the CSP would stagnate through all possible iterations. Given that, we decided to first assign all matchups between opponents that play an even number of times and only after all those were completed do we start on the 3-game matchups. This was the key to solving this CSP.
		\item Once we had our matchup we wanted to assign, we checked which values True or False were possible - if a team had reached their limit of home/away games then there was no ordering to be done. If both teams could potentially be the home team, we chose to first try the team with the fewer number of home games be the potential home team. Then, for any Home/Away assignment, we had our master dates list with potential dates. We ordered these according to the distance to the ``ideal date'', the 2*game\_num we had used to first assign the window of possible dates. The resulting list of possible assignments was interleaved True/False assignments with their associated dates based on distance to the ``ideal date''.
		\begin{itemize}
			\item As an example suppose for $(Team_1,Team_2,game\_num=10)$, the window of home dates for $Team_1$ are $(17,19,21,23)$ and the window of home dates for $Team_2$ are $(18,20)$. We want to first try $Team_2$ as the home team because to that point it's had less home assignments, so False would take priority to True. The resulting ordering of the domain would be: $[(20,False),(19,True),(18,False),(21,True),(23,True),(17,True)]$ - ordering of 19/21 and 17/23 could be flipped based Python's sort implementation.
		\end{itemize}
	\end{enumerate}

>>>>

\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{courier}
\usepackage{multicol}
\usepackage{microtype} %required to fix courier linebreaking issues
\usepackage{hyperref} % make references into links
\usepackage{amsfonts}
\hypersetup{colorlinks=true, linkcolor=blue} %make them pretty links
\usepackage[all]{hypcap} %make them link to the right place
\usepackage{url}
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother
\usepackage{geometry}
\geometry{legalpaper, portrait, margin=1.5in}

@@

	The rationale here is the season is typically 160-170 days, meaning ideally each game is every other day. So, we specify the domain of possible dates for a game to be a window of dates centered at that ideal date. The heuristics used were as follows:
	\begin{enumerate}
		\item Forward checking was relatively straightforward in this CSP. We remove any True/False possibilities for any pair of teams if one team has reached the limit of home or away games for that matchup. For any date $d$ we assign for some game\_num, we remove the dates prior to $d$ for any game after game\_num, and any date after $d$ for any game before game\_num for any matchup involving one of these teams.
		\item Choosing what matchup to next assign was the most perplexing part of this problem. We initially chose the team with the most assignments up to that point - essentially trying to assign all home/away matchups for a specific team at a time. The difficulty in this CSP is finding the right assignments for matchups of teams that play 3 times. There's an added complexity of having the right combination of 1 home/2 away and 2 home/1 away matchups that keep each team's total home/away games even. What was originally happening was the DFS would assign every matchup for every team until the last few, but it was impossible to find a right assignment for them because too many teams had their 3-game matchups with a given 2-home or 2-aways. There wasn't a good backtracking method implemented once that happened, so the CSP would stagnate through all possible iterations. Given that, we decided to first assign all matchups between opponents that play an even number of times and only after all those were completed do we start on the 3-game matchups. This was the key to solving this CSP.
		\item Once we had our matchup we wanted to assign, we checked which values True or False were possible - if a team had reached their limit of home/away games then there was no ordering to be done. If both teams could potentially be the home team, we chose to first try the team with the fewer number of home games be the potential home team. Then, for any Home/Away assignment, we had our master dates list with potential dates. We ordered these according to the distance to the ``ideal date'', the 2*game\_num we had used to first assign the window of possible dates. The resulting list of possible assignments was interleaved True/False assignments with their associated dates based on distance to the ``ideal date''.
		\begin{itemize}
			\item As an example suppose for $(Team_1,Team_2,game\_num=10)$, the window of home dates for $Team_1$ are $(17,19,21,23)$ and the window of home dates for $Team_2$ are $(18,20)$. We want to first try $Team_2$ as the home team because to that point it's had less home assignments, so False would take priority to True. The resulting ordering of the domain would be: (20,False), (19,True), (18,False), (21,True), (23,True), (17,True) - ordering of 19/21 and 17/23 could be flipped based Python's sort implementation.
		\end{itemize}
	\end{enumerate}
